---
title: "Classifying Popular Audiobooks with Logistic Regression in R"
author: "Ricky Soo"
date: "1st February 2021"
output:
  html_document:
    theme: readable
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
---

GitHub - <a href="https://github.com/rickysoo/audiobooks" target="_blank">https://github.com/rickysoo/audiobooks</a>

## Introduction

In this exercise, we are going to classify and predict popular audiobooks on Audible.com. The data has previously been sourced and cleaned in this project.

Load libraries

```{r}
library(ggplot2)
library(dplyr)
library(caret)
library(broom)
```

Load audiobook data.

```{r}
set.seed(88)

audible <- read.csv('audible_cleaned.csv')
# audible <- audible %>% sample_n(1000)
audible$Popular <- factor(audible$Popular)
```

## Explore Data

Quick check on data.

```{r}
str(audible)
table(audible$Popular)
sum(is.na(audible))
```
Explore variables using histograms. *RatingCount*, *Length* and *DaysReleased* are found to be skewed so they are log-transformed to make them more normally distributed.

```{r}
ggplot(audible, aes(x = Price, fill = Popular)) +
    geom_histogram(bins = 30)
```


```{r}
ggplot(audible, aes(x = RatingCount, fill = Popular)) +
    geom_histogram(bins = 30)
```


```{r}
audible$RatingCountLog <- log(audible$RatingCount)

ggplot(audible, aes(x = RatingCountLog, fill = Popular)) +
    geom_histogram(bins = 30)
```

```{r}
ggplot(audible, aes(x = Length, fill = Popular)) +
    geom_histogram(bins = 30)
```

```{r}
audible$LengthLog <- log(audible$Length)

ggplot(audible, aes(x = LengthLog, fill = Popular)) +
    geom_histogram(bins = 30)
```

```{r}
ggplot(audible, aes(x = DaysReleased, fill = Popular)) +
    geom_histogram(bins = 30)
```

```{r}
audible$DaysReleasedLog <- log(max(audible$DaysReleased) + 1 - audible$DaysReleased)

ggplot(audible, aes(x = DaysReleasedLog, fill = Popular)) +
    geom_histogram(bins = 30)
```

Explore *Category* using bar plot. Self-development books are found to have a high proportion of popular books. A new variable *SelfDevelopment* is added to possibly capture this pattern in model training.

```{r}
ggplot(audible, aes(y = Category, fill = Popular)) +
    geom_bar(stat = 'count')
```

```{r}
audible$SelfDevelopment <- ifelse(audible$Category == 'Self Development', 1, 0)
table(audible$SelfDevelopment)
```

```{r}
saveRDS(audible, 'audible-complete.rds')
audible <- audible[c('Price', 'RatingCountLog', 'LengthLog', 'DaysReleasedLog', 'SelfDevelopment', 'Popular')]
```

## Train Data

Split data for training.

```{r}
samples <- createDataPartition(audible$Popular, p = 0.8, list = FALSE)
train.data <- audible[samples, ]
test.data <- audible[-samples, ]
```

Training a classification model using logistic regression.

```{r}
model <- glm(Popular ~ Price + RatingCountLog + LengthLog + DaysReleasedLog + SelfDevelopment, data = train.data, family = binomial)
summary(model)
```
Check the accuracy of prediction.

```{r}
test_probabilities <- predict(model, test.data, type = 'response')
test_popular <- ifelse(test_probabilities > 0.5, 1, 0)
accuracy <- mean(test_popular == test.data$Popular)
accuracy
```
Check the classification matrix.

```{r}
test_popular <- as.factor(test_popular)
CM <- confusionMatrix(test_popular, test.data$Popular, positive = '1')
fourfoldplot(CM$table)
```

```{r}
table(test_popular, test.data$Popular)
prop.table(table(test_popular, test.data$Popular))
```

## Save Model

Make prediction on all audiobooks.

```{r}
probabilities <- predict(model, audible, type = 'response')
audible$Predicted <- ifelse(probabilities > 0.5, 1, 0)
accuracy <- mean(audible$Predicted == audible$Popular)
accuracy
```
```{r}
audible$Predicted <- as.factor(audible$Predicted)
CM <- confusionMatrix(audible$Predicted, audible$Popular, positive = '1')
fourfoldplot(CM$table)
```

```{r}
table(audible$Predicted, audible$Popular)
prop.table(table(audible$Predicted, audible$Popular))
```
Save model for future use.

```{r}
saveRDS(model, 'model-LR.rds')
```
